The Essence of Summarization\\ in Pushdown Flow Analyses\\ \textbf{Supplemental Material}

### 2013-12-13 abstract.tex
Started a section on with-continuation-mark, but had to punt due to extension vs copy adding more complexity than I could fit.

Pushdown analysis improves upon finite-state analysis in precision and performance by not exploring spurious paths caused by improperly matched calls and returns.
%
Prior literature on pushdown higher-order flow analysis depends on complicated machinery that is difficult to understand, extend, and prove correct.
%
The machinery has no concrete counterpart --- there is little to no operational intuition as to why it works.
%
We show that these pushdown analyses have a similar core that can be explained with well-known techniques such as memoization and Abstracting Abstract Machines (AAM).
%
We use this interpretation to derive a novel pushdown analysis for delimited, composable control.

>>>>

Pushdown analysis improves upon finite-state analysis in precision and performance by not exploring spurious paths caused by improperly matched calls and returns.
%
Prior literature on pushdown higher-order flow analysis depends on complicated machinery that is difficult to understand, extend, and prove correct.
%
The machinery has no concrete counterpart---there is little to no operational intuition as to why it works.
%
We show that these pushdown analyses have a similar core that can be explained with well-known techniques such as memoization and Abstracting Abstract Machines (AAM).
%
We use this interpretation to derive novel pushdown analyses for delimited, composable control.
